\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2013-12-16 doc/paper.tex

\item Add Singlet Higgs superfield to SuperField
\begin{lstlisting}
SuperFields[[8]] = {s, 1, sR,     0, 1,  1, 5, RpP};
\end{lstlisting}
\item Add inert Higgs-like superfields 
\begin{lstlisting}
SuperFields[[9]] = {H1I, 2, {H1I0, H1Im},  -1/2, 2, 1, -3, RpP};
SuperFields[[10]] = {H2I, 2, {H2Ip, H2I0},   1/2, 2, 1, -2, RpP};
SuperFields[[11]] = {sI, 2, sIR,    0, 1,  1, 5, RpM};
\end{lstlisting}
\item Add exotics to SuperFields
\begin{lstlisting}
SuperFields[[12]] = {Dx, 3, DxL,  -1/3, 1, 3, -2, RpP};
SuperFields[[13]] = {Dxbar, 3, conj[DxbarR],  1/3, 1, -3, -3, RpP};
\end{lstlisting}
\item Add additional survival $SU(2)$ multiplets to SuperFields
\begin{lstlisting}
SuperFields[[14]] = {Hp, 1, {Hpd0, Hpdm},  1/2, 2,  1, 2, RpP};
SuperFields[[15]] = {Hpbar, 1, {Hpup, Hpu0}, -1/2, 2,  1, -2, RpP};
\end{lstlisting}
\item Modify superpotential
\begin{lstlisting}
SuperPotential = Yu u.q.Hu - Yd d.q.Hd - Ye e.l.Hd + \[Lambda] s.Hu.Hd +  \[Lambda]12 s.H2I.H1I + \[Kappa] s.Dx.Dxbar + \[Mu]Pr Hp.Hpbar;
\end{lstlisting}
\item Define new gauge eigenstate Dirac spinors
\begin{lstlisting}
  DEFINITION[GaugeES][DiracSpinors]={
    .............
    .............
    FS -> {FsR,conj[FsR]},
    FBp -> {fBp,conj[fBp]},
    HI0 -> {FH1I0, conj[FH2I0]},
    HIC -> {FH1Im, conj[FH2Ip]},
    FSI -> {FsIR, conj[FsIR]},
    FDx1 -> {FDxL, 0},
    FDx2 -> {0, FDxbarR}, 
    Hp0 -> {FHpd0, conj[FHpu0]},
    HpC -> {FHpdm, conj[FHpup]}
  };
\end{lstlisting}
\item Add new VEV
\begin{lstlisting} 
  DEFINITION[EWSB][VEVs]= 
  { {SHd0, {vd, 1/Sqrt[2]}, {sigmad, \[ImaginaryI]/Sqrt[2]},{phid,1/Sqrt[2]}},
    {SHu0, {vu, 1/Sqrt[2]}, {sigmau, \[ImaginaryI]/Sqrt[2]},{phiu,1/Sqrt[2]}},
    {SsR,  {vs, 1/Sqrt[2]}, {sigmaS, \[ImaginaryI]/Sqrt[2]},{phiS,1/Sqrt[2]}}
};
\end{lstlisting}
\item Add new gauge boson  mass eigenstate
\begin{lstlisting} 
  DEFINITION[EWSB][GaugeSector] =
  { 
    {{VB,VWB[3],VBp},{VP,VZ,VZp},ZZ},
    {{VWB[1],VWB[2]},{VWm,conj[VWm]},ZW},
    {{fWB[1],fWB[2],fWB[3]},{fWm,fWp,fW0},ZfW}
  }; 
\end{lstlisting}
\item Edit mixings for Higgs and neutralino states and add additional states that mix.
\begin{lstlisting}
DEFINITION[EWSB][MatterSector]= 
{ ...............
  ...............
{{phid, phiu, phiS}, {hh, ZH}},
{{sigmad, sigmau, sigmaS}, {Ah, ZA}},
  ...............
{{fB, fW0, FHd0, FHu0, FsR, fBp}, {L0, ZN}},
 ................ 
 {{SH1I0,conj[SH2I0]},{SHI0,UHI0}},
 {{SH1Im,conj[SH2Ip]},{SHIp,UHIp}},
 {{SHpd0,conj[SHpu0]},{SHp0,UHp0}},
 {{SHpdm,conj[SHpup]},{SHpp,UHpp}},
 {{FHpd0,FHpu0},{L0p,ZNp}},
 {{FH1I0,FH2I0},{L0I,ZNp}}
\end{lstlisting}
\end{enumerate}

>>>>

\item Add Singlet Higgs superfield to SuperField
\begin{lstlisting}
SuperFields[[8]] = {s, 1, sR,     0, 1,  1, 5, RpP};
\end{lstlisting}
\item Add inert Higgs-like superfields 
\begin{lstlisting}
SuperFields[[9]] = {H1I, 2, {H1I0, H1Im},  -1/2, 2, 1, -3, RpP};
SuperFields[[10]] = {H2I, 2, {H2Ip, H2I0},   1/2, 2, 1, -2, RpP};
SuperFields[[11]] = {sI, 2, sIR,    0, 1,  1, 5, RpM};
\end{lstlisting}
\item Add exotics to SuperFields
\begin{lstlisting}
SuperFields[[12]] = {Dx, 3, DxL,  -1/3, 1, 3, -2, RpP};
SuperFields[[13]] = {Dxbar, 3, conj[DxbarR],  1/3, 1, -3, -3, RpP};
\end{lstlisting}
\item Add additional survival $SU(2)$ multiplets to SuperFields
\begin{lstlisting}
SuperFields[[14]] = {Hp, 1, {Hpd0, Hpdm},  1/2, 2,  1, 2, RpP};
SuperFields[[15]] = {Hpbar, 1, {Hpup, Hpu0}, -1/2, 2,  1, -2, RpP};
\end{lstlisting}
\item Modify superpotential
\begin{lstlisting}
SuperPotential = Yu u.q.Hu - Yd d.q.Hd - Ye e.l.Hd + \[Lambda] s.Hu.Hd +  \[Lambda]12 s.H2I.H1I + \[Kappa] s.Dx.Dxbar + \[Mu]Pr Hp.Hpbar;
\end{lstlisting}
\item Define new gauge eigenstate Dirac spinors
\begin{lstlisting}
  DEFINITION[GaugeES][DiracSpinors]={
    .............
    .............
    FS -> {FsR,conj[FsR]},
    FBp -> {fBp,conj[fBp]},
    HI0 -> {FH1I0, conj[FH2I0]},
    HIC -> {FH1Im, conj[FH2Ip]},
    FSI -> {FsIR, conj[FsIR]},
    FDx1 -> {FDxL, 0},
    FDx2 -> {0, FDxbarR}, 
    Hp0 -> {FHpd0, conj[FHpu0]},
    HpC -> {FHpdm, conj[FHpup]}
  };
\end{lstlisting}
\item Add new VEV
\begin{lstlisting} 
  DEFINITION[EWSB][VEVs]= 
  { {SHd0, {vd, 1/Sqrt[2]}, {sigmad, \[ImaginaryI]/Sqrt[2]},{phid,1/Sqrt[2]}},
    {SHu0, {vu, 1/Sqrt[2]}, {sigmau, \[ImaginaryI]/Sqrt[2]},{phiu,1/Sqrt[2]}},
    {SsR,  {vs, 1/Sqrt[2]}, {sigmaS, \[ImaginaryI]/Sqrt[2]},{phiS,1/Sqrt[2]}}
};
\end{lstlisting}
\item Add new gauge boson  mass eigenstate
\begin{lstlisting} 
  DEFINITION[EWSB][GaugeSector] =
  { 
    {{VB,VWB[3],VBp},{VP,VZ,VZp},ZZ},
    {{VWB[1],VWB[2]},{VWm,conj[VWm]},ZW},
    {{fWB[1],fWB[2],fWB[3]},{fWm,fWp,fW0},ZfW}
  }; 
\end{lstlisting}
\item Edit mixings for Higgs and neutralino states and add additional states that mix.
\begin{lstlisting}
DEFINITION[EWSB][MatterSector]= 
{ ...............
  ...............
{{phid, phiu, phiS}, {hh, ZH}},
{{sigmad, sigmau, sigmaS}, {Ah, ZA}},
  ...............
{{fB, fW0, FHd0, FHu0, FsR, fBp}, {L0, ZN}},
 ................ 
 {{SH1I0,conj[SH2I0]},{SHI0,UHI0}},
 {{SH1Im,conj[SH2Ip]},{SHIp,UHIp}},
 {{SHpd0,conj[SHpu0]},{SHp0,UHp0}},
 {{SHpdm,conj[SHpup]},{SHpp,UHpp}},
 {{FHpd0,FHpu0},{L0p,ZNp}},
 {{FH1I0,FH2I0},{L0I,ZNI}}
\end{lstlisting}
\end{enumerate}
